Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-18 tex/paper1/paper1.tex
updated fit parameter table
added in some chi-squared stuff

\begin{deluxetable}{cccccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.  {\bf Uncertainties with an absolute value less than $0.005$ are quoted as $0.00$.} \label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & 
\multicolumn{3}{c}{lognormal $G(\nu)$} & 
\multicolumn{2}{c}{ratio $P_{1}(\nu)/G(\nu)$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$ (mHz)}      &
\colhead{$\delta$\tablenotemark{1}} &
\colhead{$\max$}          & 
\colhead{$\arg\max$ (mHz)}
\\
}
\startdata
loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.28^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.34^{+0.07}_{-0.07}$ & $0.73^{+0.07}_{-0.06}$  & $0.32^{+0.01}_{-0.01}$    & & \\
                & 193\AA  & $0.06^{+0.02}_{-0.02}$  & $2.26^{+0.04}_{-0.04}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.30^{+0.18}_{-0.20}$ & $0.34^{+0.12}_{-0.08}$  & $0.41^{+0.03}_{-0.03}$  & & \\
                & & & & & & &   & & \\

moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$    & & \\
                & 193\AA  & $0.40^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.59^{+0.00}_{-0.00}$  & $-2.01^{+0.02}_{-0.03}$  & $1.25^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$    & & \\
                & & & & & & &   & & \\

quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$    & & \\
                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.51^{+0.00}_{-0.00}$  & $-4.74^{+0.06}_{-0.06}$  & $4.68^{-0.18}_{-0.18}$  & $0.11^{+0.01}_{-0.01}$    & & \\
                & & & & & & &   & & \\

sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.02}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.78^{+0.02}_{-0.02}$  & $1.80^{+0.06}_{-0.06}$  & $0.33^{+0.01}_{-0.01}$    & & \\
                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.13^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.05^{+0.03}_{-0.02}$  & $1.62^{+0.6}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$   & &  \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.
\tablenotetext{1}{Values are quoted in decades of frequency}
\end{deluxetable}

@@

{\bf The two models are assessed for how well they describe the data in two
different ways. Model selection is implemented using the Akaike Information Criterion
(AIC; \citealp*{akaike}).  The AIC measures the amount of information
lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv 2k -2 \ln L_{max}
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  Model selection is guided by calculating
$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
AIC$ indicate that Model 2 loses less information compared to Model 1,
leading to a preference for Model 2 over Model 1
\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}

{\bf The AIC reveals which out of a set of models is preferred.  It
  does not give an assessment of the goodness-of-fit of each model.
  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$ is
  calculated for both models.}

Table \ref{tab:parameters} gives the parameter estimates and 68\%
credible intervals of the parameter values for model $M_{2}$.  The
power law indices for all regions and both wavebands lie in the range
1.8 to 2.3, although there is no consistency between one waveband and
another.  For example, the 171\AA\ and 193\AA\ loop footpoint results
both have the same power law index, but the other regions do not.
However, it should be noted that there is no {\it a priori} reason why
the power law indices for a region seen in two different wavebands
should be the same.  This is because each waveband is designed to
examine different features on the Sun in broadly different temperature
ranges, and may be imaging very different physical processes: hence,
the emission seen in one waveband need not have the same statistical
properties as any other.

>>>>

\begin{deluxetable}{cccccccccc}
\tabletypesize{\scriptsize}
\tablecolumns{5}
\tablewidth{0pt}
\tablecaption{Parameter values and uncertainty estimates derived for
    model \protect$M_{2}$.  {\bf Uncertainties with an absolute value less than $0.005$ are quoted as $0.00$.} \label{tab:parameters}}
\tablehead{
\colhead{Region} & 
\colhead{Waveband}    & 
\multicolumn{3}{c}{\PL\ $P_{1}(\nu)$} & 
\multicolumn{3}{c}{lognormal $G(\nu)$} & 
\multicolumn{2}{c}{ratio $P_{1}(\nu)/G(\nu)$}\\
\colhead{}          & 
\colhead{}          & 
\colhead{$\log_{10}A$}          & 
\colhead{$n$}      & 
\colhead{$\log_{10}C$}      &
\colhead{$\log_{10}\alpha$} &
\colhead{$\beta$ (mHz)}      &
\colhead{$\delta$\tablenotemark{1}} &
\colhead{$\max$}          & 
\colhead{$\arg\max$ (mHz)}
\\
}
\startdata
loop footpoints & 171\AA  & $0.55^{+0.02}_{-0.02}$  & $2.29^{+0.02}_{-0.02}$  & $-4.26^{+0.00}_{-0.00}$  & $-2.30^{+0.09}_{-0.08}$ & $0.69^{+0.09}_{-0.08}$  & $0.32^{+0.01}_{-0.01}$    & 1.45 & 2.22 \\
                & 193\AA  & $0.06^{+0.03}_{-0.02}$  & $2.28^{+0.04}_{-0.05}$ & $-4.40^{+0.00}_{-0.00}$  & $-2.18^{+0.16}_{-0.22}$ & $0.28^{+0.11}_{-0.06}$  & $0.43^{+0.03}_{-0.04}$  & 1.58 & 1.90 \\
                & & & & & & &   & & \\

moss            & 171\AA  & $0.29^{+0.01}_{-0.01}$  & $1.76^{+0.01}_{-0.01}$ & $-4.04^{+0.00}_{-0.00}$  & $-1.34^{+0.02}_{-0.02}$  & $0.88^{+0.02}_{-0.02}$  & $0.34^{+0.00}_{-0.00}$    & 5.19 & 2.45\\
                & 193\AA  & $0.39^{+0.01}_{-0.01}$  & $2.05^{+0.01}_{-0.01}$ & $-4.49^{+0.00}_{-0.00}$  & $-2.00^{+0.02}_{-0.02}$  & $1.24^{+0.03}_{-0.03}$  & $0.27^{+0.00}_{-0.00}$    & 4.72 & 2.68 \\
                & & & & & & &   & & \\

quiet Sun       & 171\AA  & $0.57^{+0.01}_{-0.01}$  & $1.72^{+0.01}_{-0.01}$ & $-3.00^{+0.00}_{-0.00}$  & $-3.55^{+0.04}_{-0.04}$  & $4.41^{+0.08}_{-0.08}$  & $0.10^{+0.01}_{-0.01}$    & 0.20 & 4.63 \\
                & 193\AA  & $-0.10^{+0.01}_{-0.01}$  & $2.20^{+0.01}_{-0.01}$ & $-3.52^{+0.00}_{-0.00}$  & $-4.75^{+0.05}_{-0.05}$  & $4.68^{+0.18}_{-0.17}$  & $0.11^{+0.01}_{-0.01}$    & 0.08 & 4.72 \\
                & & & & & & &   & & \\

sunspot         & 171\AA  & $0.43^{+0.01}_{-0.01}$  & $2.26^{+0.02}_{-0.01}$ & $-3.89^{+0.00}_{-0.00}$  & $-2.80^{+0.02}_{-0.02}$  & $1.83^{+0.05}_{-0.05}$  & $0.32^{+0.00}_{-0.00}$    & 2.07 & 3.56 \\
                & 193\AA  & $-0.09^{+0.01}_{-0.01}$  & $2.14^{+0.02}_{-0.02}$ & $-3.97^{+0.00}_{-0.00}$  & $-3.04^{+0.03}_{-0.03}$  & $1.59^{+0.07}_{-0.07}$  & $0.35^{+0.01}_{-0.01}$   & 1.55 & 3.15 \\
\enddata
%% Text for table notes should follow after the \enddata but before
%% the \end{deluxetable}. Make sure there is at least one \tablenotemark
%% in the table for each \tablenotetext.
\tablenotetext{1}{Values are quoted in decades of frequency}
\end{deluxetable}

@@

{\bf The two models are assessed for how well they describe the data in two
different ways. Model selection is implemented using the Akaike Information Criterion
(AIC; \citealp*{akaike}).  The AIC measures the amount of information
lost when fitting a model to data \citep{2000Ap&SS.271..213T}.  The
AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv 2k -2 \ln L_{max}
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  Model selection is guided by calculating
$\triangle AIC = AIC_{1} - AIC_{2}$.  Positive values of $\triangle
AIC$ indicate that Model 2 loses less information compared to Model 1,
leading to a preference for Model 2 over Model 1
\citep{2007MNRAS.377L..74L}.  The AIC indicates that Model 2 is
overwhelmingly preferred to Model 1 (see Figure \ref{fig:fit171193}).}
{\bf The AIC reveals which out of a set of models is preferred.  It
  does not give an assessment of the goodness-of-fit of each model.
  Goodness-of-fit is estimated by calculating reduced-$\chi^{2}$,
  $\chi^{2}_{r}=\sum_{i=1}^{N}\left[(P(\nu_{i})-D_{i})/\sigma_{i}^{2}\right]$
  is calculated for both models.  The $\chi^{2}_{r}$ measures show
  that reasonable fits are obtained for Model $M_{2}$ in all cases,
  excepting the loop footpoints.  The relatively low value of $\chi^{2}_{r}$}

Table \ref{tab:parameters} gives the parameter estimates and 68\%
credible intervals of the parameter values for model $M_{2}$, {\bf the
  maximum value of the ratio $G(\nu)/P_{1}(\nu)$ and its location}.
The power law indices for all regions and both wavebands lie in the
range 1.8 to 2.3, although there is no consistency between one
waveband and another.  For example, the 171\AA\ and 193\AA\ loop
footpoint results both have the same power law index, but the other
regions do not.  However, it should be noted that there is no {\it a
  priori} reason why the power law indices for a region seen in two
different wavebands should be the same.  This is because each waveband
is designed to examine different features on the Sun in broadly
different temperature ranges, and may be imaging very different
physical processes: hence, the emission seen in one waveband need not
have the same statistical properties as any other.
